---
title: "Visualizing traffic accidents from FARS data"
author: "João Santiago"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(FARSr)
```


The US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS) is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. This package will help you run some quick analyses and plot accidents on a map, for the county of your choosing.

## Summarize number of accidents

The *fars_summarize_years* function shows the number of accidents per month, per year. This is a quick way to see summarize the data and get a first impression. Make sure your data files are in your working directory, and have the format *accident_YEAR.csv.bz2*.
```{r}
fars_2013_2014 <- fars_summarize_years(c(2013, 2014))

head(fars_2013_2014)
```


## Plot accidents on a map

The main feature of the \code{FARSr} package is the ability to make a map of all accidents, for a period of time in a chosen county. For this you use the \code{fars_map_state} function, which takes as inputs the code for the county of interest and a year.
 
```{r}
fars_map_state(1, 2014)
```
